Wikipedia ngrams Entropy Analysis

### 2019-04-18 ngrams/wiki_ngrams.Rmd
reorganized wikipedia ngrams data

```{r setup, include=FALSE}
library(tidyverse)
library(tidytext)
library(googlesheets)
library(here)
library(feather)
library(magrittr)
library(reshape2)
library(lme4)

@@

```{r getting gsheets}
w1 <- read_feather(here("relative_unigrams.feather"))
w2 <- read_feather(here("relative_bigrams.feather"))
w3 <- read_feather(here("relative_trigrams.feather"))
w4 <- read_feather(here("relative_quadgrams.feather"))

@@

w1 %>% 
  left_join(w2) %>%
  left_join(w3) %>%
  left_join(w4) %>%
  remove_missing() %>%
  slice(1:5) %>%
  melt(id.vars = "Language") %>%
  ggplot(aes(variable, value, color=Language)) + 
  geom_point() +
  geom_line()
```

# let's just try log(sum(abs(s_i))) = language + gram since type/source are all the same atm
## why would there be an interaction between language and gram?

>>>>

```{r setup, include=FALSE}
library(tidyverse)
library(tidytext)
library(here)
library(feather)
library(magrittr)
library(reshape2)
library(lme4)

@@

```{r set up data}
w1 %>% 
  left_join(w2) %>%
  left_join(w3) %>%
  left_join(w4) %>%
  remove_missing() %>%
  slice(1:5) %>%
  melt(id.vars = "Language") %>%
  ggplot(aes(variable, value, color=Language)) + 
  geom_point() +
  geom_line()
```

# let's just try log(sum(abs(s_i))) = language + gram since type/source are all the same atm
## why would there be an interaction between language and gram?
wn <- read_feather(here("Data/wiki_ngrams.feather"))

```{r get data}
w1 <- read_feather(here("Data/relative_unigrams.feather"))
w2 <- read_feather(here("Data/relative_bigrams.feather"))
w3 <- read_feather(here("Data/relative_trigrams.feather"))
w4 <- read_feather(here("Data/relative_quadgrams.feather"))

@@

wn %>% write_feather(here("Data/wiki_ngrams.feather"))
```
